{How do we copy and paste?\\The semantic drift of quotations in blogspace}

### 2014-12-12 brains-protocol.tex
clarified 4.1b

This measure focuses on the selection of start words involved in substitutions, measuring the effect of features at the moment preceding the substitution when it is not yet known which word in the quotation will be substituted.

@@

>>>>

Put shortly, susceptibility focuses on the selection of start words involved in substitutions, measuring the effect of features at the moment preceding the substitution when it is not yet known which word in the quotation will be substituted.

\medskip
Results are gathered on Fig.~\ref{fig:feature-susceptibilities}.

@@

\medskip
Results are gathered on Fig.~\ref{fig:feature-variations}.
